Check matrix correlations

### 2018-06-20 Analysis/04-CheckMatrixCorrelation.Rmd
added libraries
Added statistics table

```{r}
library(ape)
## Setting the path
PATH <- "../Data/Simulations/Matrices/"
```

@@

## Extracting the statistic and the p_value only
wilcox_scen_w <- unlist(lapply(wilcox_scen, function(X) return(unname(X$statistic))))
wilcox_taxa_w <- unlist(lapply(wilcox_taxa, function(X) return(unname(X$statistic))))
wilcox_char_w <- unlist(lapply(wilcox_char, function(X) return(unname(X$statistic))))
wilcox_scen_p <- unlist(lapply(wilcox_scen, function(X) return(X$p.value)))
wilcox_taxa_p <- unlist(lapply(wilcox_taxa, function(X) return(X$p.value)))
wilcox_char_p <- unlist(lapply(wilcox_char, function(X) return(X$p.value)))

@@

@@

```{r, echo = FALSE}
kable(data.frame("Statistic" = wilcox_scen_w, "p_value" = wilcox_scen_p), digits = 3, 
      caption = "Pairwise Wilcoxon test for the different number of scenarios.")
kable(data.frame("bhatt.coeff" = bhattc_scen), digits = 3, 
      caption = "Pairwise Bhattacharrya Coefficient for the different number of scenarios.")

kable(data.frame("Statistic" = wilcox_taxa_w, "p_value" = wilcox_taxa_p), digits = 3, 
      caption = "Pairwise Wilcoxon test for the different number of taxa.")
kable(data.frame("bhatt.coeff" = bhattc_taxa), digits = 3, 
      caption = "Pairwise Bhattacharrya Coefficient for the different number of taxa.")

kable(data.frame("Statistic" = wilcox_char_w, "p_value" = wilcox_char_p), digits = 3, 
      caption = "Pairwise Wilcoxon test for the different number of characters.")
kable(data.frame("bhatt.coeff" = bhattc_char), digits = 3, 
      caption = "Pairwise Bhattacharrya Coefficient for the different number of characters.")
```

>>>>

```{r}
library(dispRity)
library(ape)
library(knitr)
## Setting the path
PATH <- "../Data/Simulations/Matrices/"
```

@@

## Extracting the statistic and the p_value only
wilcox_scen_w <- unlist(lapply(wilcox_scen, function(X) return(unname(X$statistic))))
wilcox_taxa_w <- unlist(lapply(wilcox_taxa, function(X) return(unname(X$statistic))))
wilcox_char_w <- unlist(lapply(wilcox_char, function(X) return(unname(X$statistic))))
wilcox_scen_p <- p.adjust(unlist(lapply(wilcox_scen, function(X) return(X$p.value))), "bonferroni")
wilcox_taxa_p <- p.adjust(unlist(lapply(wilcox_taxa, function(X) return(X$p.value))), "bonferroni")
wilcox_char_p <- p.adjust(unlist(lapply(wilcox_char, function(X) return(X$p.value))), "bonferroni")

@@

## Combine the results
combined_results <- as.data.frame(rbind(
        cbind("statistic" = wilcox_scen_w, "p.value" = wilcox_scen_p, "bhatt.coeff" = bhattc_scen),
        cbind("statistic" = wilcox_taxa_w, "p.value" = wilcox_taxa_p, "bhatt.coeff" = bhattc_taxa),
        cbind("statistic" = wilcox_char_w, "p.value" = wilcox_char_p, "bhatt.coeff" = bhattc_char)))
```

@@

```{r, echo = FALSE}
caption <- paste0("Pairwise Wilcoxon test and Bhattacharrya Coefficients for the difference in",
  " proportion of character replacement for the different scenarios, number of taxa and characters.")
kable(combined_results, digits = 3, caption = caption)
```

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
library(xtable)
source("../Functions/make.xtable.R")
make.xtable(combined_results, caption = caption, label = "Tab_proportion_replacement",
            path = "../Writing/Tables/", include.rownames = TRUE)
```
